The \dealii{} Library, Version 9.0

### 2018-04-04 9.0/paper.tex
add myself, add a couple of points

\author[4]{Timo Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
% 
% \author[5]{Luca Heltai}
% \affil[5]{SISSA,
%   International School for Advanced Studies,
%   Via Bonomea 265,
%   34136, Trieste, Italy.
% {\texttt{luca.heltai@sissa.it}}}
% 
% \author[6]{Martin Kronbichler}
% \affil[6]{Institute for Computational Mechanics,
%   Technical University of Munich,
%   Boltzmannstr.~15, 85748 Garching, Germany.
%   {\texttt{kronbichler@lnm.mw.tum.de}}}
% 
% \author[7]{Matthias Maier}
% \affil[7]{School of Mathematics,
%   University of Minnesota,
%   127 Vincent Hall, 206 Church Street SE,
%   Minneapolis, MN 55455, USA.
%   {\texttt{msmaier@umn.edu}}}
% 
% \author[8]{Jean-Paul Pelteret}
% \affil[8]{Chair of Applied Mechanics,
%   University of Erlangen-Nuremberg,
%   Egerlandstr.\ 5,
%   91058 Erlangen,
%   Germany.
%   {\texttt{jean-paul.pelteret@fau.de}}}
% 
% \author[9]{Bruno Turcksin\footnote{
%   This manuscript has been authored by UT-Battelle, LLC under Contract No.
%   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
%   Government retains and the publisher, by accepting the article for
%   publication, acknowledges that the United States Government retains a
%   non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
%   the published form of this manuscript, or allow others to do so, for United
%   States Government purposes. The Department of Energy will provide public
%   access to these results of federally sponsored research in accordance with the
%   DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
% \affil[9]{Computational Engineering and Energy Sciences Group,
%   Computional Sciences and Engineering Division,
%   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
%   TN 37831, USA.
%   {\texttt{turcksinbr@ornl.gov}}}
% 
% \author[10]{David Wells}
% \affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
% Troy, NY 12180, USA.
%   {\texttt{wellsd2@rpi.edu}}}

@@

\item

>>>>

\author[4]{Timo Heister}
\affil[4]{Mathematical Sciences,
  O-110 Martin Hall,
  Clemson University,
  Clemson, SC 29634, USA.
  {\texttt{heister@clemson.edu}}}
% 
% \author[5]{Luca Heltai}
% \affil[5]{SISSA,
%   International School for Advanced Studies,
%   Via Bonomea 265,
%   34136, Trieste, Italy.
% {\texttt{luca.heltai@sissa.it}}}
% 
% \author[6]{Martin Kronbichler}
% \affil[6]{Institute for Computational Mechanics,
%   Technical University of Munich,
%   Boltzmannstr.~15, 85748 Garching, Germany.
%   {\texttt{kronbichler@lnm.mw.tum.de}}}
% 
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA.
  {\texttt{msmaier@umn.edu}}}
% 
% \author[8]{Jean-Paul Pelteret}
% \affil[8]{Chair of Applied Mechanics,
%   University of Erlangen-Nuremberg,
%   Egerlandstr.\ 5,
%   91058 Erlangen,
%   Germany.
%   {\texttt{jean-paul.pelteret@fau.de}}}
% 
% \author[9]{Bruno Turcksin\footnote{
%   This manuscript has been authored by UT-Battelle, LLC under Contract No.
%   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
%   Government retains and the publisher, by accepting the article for
%   publication, acknowledges that the United States Government retains a
%   non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
%   the published form of this manuscript, or allow others to do so, for United
%   States Government purposes. The Department of Energy will provide public
%   access to these results of federally sponsored research in accordance with the
%   DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
% \affil[9]{Computational Engineering and Energy Sciences Group,
%   Computional Sciences and Engineering Division,
%   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
%   TN 37831, USA.
%   {\texttt{turcksinbr@ornl.gov}}}
% 
% \author[10]{David Wells}
% \affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
% Troy, NY 12180, USA.
%   {\texttt{wellsd2@rpi.edu}}}

@@

\item
  Improved support for LinearOperator (Trilinos payload, Schur complement,
  iterative inverse), removal of old wrapper classes

\item
  Initial support for generalized support points: Internal interpolation
  rewritten (support for $H(\text{curl})$ and $H(\text{div})$ conforming
  elements).
